### 2018-07-23 express2018/equa.tex
Fixed p.4, “In contrast, ...”: #31

For instance, the solution of the equation 
$ X = a. X$ 
is  the process
$R \DSdefi \recu A { a. A}$, and   for any other solution $P$ we have $P \wb R$.
In contrast, the equation 
 $X = a|  X$ has solutions that may be quite different, namely any process capable of
continuously  performing $a$ actions (but that could behave arbitrarily  on other actions).

>>>>

For instance, the solution of the equation 
$ X = a. X$ 
is  the process
$R \DSdefi \recu A {\, (a. A)}$, and for any other solution $P$ we have $P \wb R$.
In contrast, the equation 
 $X = a|  X$ has solutions that may be quite different, for instance,
 $K$ and $K | b$, for $K \DSdefi \recu K {\, (a. K)}$. (Actually any process capable of
continuously performing $a$ actions (while behaves arbitrarily on
other actions) is a solution for $X = a|  X$.)
